Comparing fluorometric methods ( in vivo vs extracted) for cyanoHAB monitoring in six Rhode Island ponds

### 2024-08-02 manuscript/manuscript.qmd
updated manuscript based on MC comments

![Comparison of fluorometer measurements of chlorophyll by waterbody. Blue lines represent the best fit regression line. R^2^ on plot is the coeffecient of determination for this line.](images/fig2_chla_scatter.jpg){#fig-chlascatter width="8.5in" height="5.25in"}

```{r chl_summary, results='asis', echo=FALSE, message=FALSE}
#| label: tbl-chlsummary
#| tbl-cap: "Summary of extracted chlorophyll from Turner Trilogy by waterbody."

@@

![Comparison of fluorometer measurements of phycocyanin by waterbody. Blue lines represent the best fit regression line. R^2^ on plot is the coeffecient of determination for this line.](images/fig3_phyco_scatter.jpg){#fig-phycoscatter width="8.5in" height="5.25in"}

```{r phyco_summary, results='asis', echo=FALSE, message=FALSE}
#| label: tbl-phycosummary
#| tbl-cap: "Summary of extracted phycocyanin from Turner Trilogy by waterbody."

@@

![Compare fluorometer chlorophyll to cyanobacteria cell counts. Blue lines represent the best fit regression line. R^2^ on plot is the coeffecient of determination for this line.](images/fig5_chl_vs_cells.jpg){#fig-chlcount width="8.5in" height="5.25in"}

![Compare fluorometer phycocyanin to cyanobacteria cell counts. Blue lines represent the best fit regression line. R^2^ on plot is the coeffecient of determination for this line.](images/fig6_phyco_vs_cells.jpg){#fig-phycocount width="8.5in" height="5.25in"}

>>>>

![Comparison of fluorometer measurements of chlorophyll by waterbody. Blue lines represent the best fit regression line. R^2^ on plot is the coefficient of determination for this line.](images/fig2_chla_scatter.jpg){#fig-chlascatter width="8.5in" height="5.25in"}

```{r chl_summary, results='asis', echo=FALSE, message=FALSE}
#| label: tbl-chlsummary
#| tbl-cap: "Summary (mean and standard deviation) of extracted chlorophyll from Turner Trilogy for waterbodies sampled in Rhode Island."

@@

![Comparison of fluorometer measurements of phycocyanin by Rhode Island waterbody. Blue lines represent the best fit regression line. R^2^ on plot is the coefficient of determination for this line.](images/fig3_phyco_scatter.jpg){#fig-phycoscatter width="8.5in" height="5.25in"}

```{r phyco_summary, results='asis', echo=FALSE, message=FALSE}
#| label: tbl-phycosummary
#| tbl-cap: "Summary (mean and standard deviation) of extracted phycocyanin from Turner Trilogy for waterbodies sampled in Rhode Island."

@@

![Comparison of fluorometer chlorophyll to cyanobacteria cell counts. Blue lines represent the best fit regression line. R^2^ on plot is the coefficient of determination for this line.](images/fig5_chl_vs_cells.jpg){#fig-chlcount width="8.5in" height="5.25in"}

![Comparison of fluorometer phycocyanin to cyanobacteria cell counts. Blue lines represent the best fit regression line. R^2^ on plot is the coefficient of determination for this line.](images/fig6_phyco_vs_cells.jpg){#fig-phycocount width="8.5in" height="5.25in"}
